Data Archiving Attitudes

### 2015-05-27 analysis.Rmd
Added plots for all relevant questions.

load("./data/JDAP_Survey_Data_Tidy.rda") # loads 'd'
load("./data/Journal_JDAP_Adoption_Dates.rda") # loads 'dates'
load("./data/Invitations_Timing.rda") # loads 'invitation_timing'
interactive_mode <- FALSE

@@

_(Strongly Agree - Agree - Somewhat Agree - Neutral - Somewhat Disagree - Disagree - Strongly Disagree)_

_(Strongly Agree - Agree - Somewhat Agree - Neutral - Somewhat Disagree - Disagree - Strongly Disagree)_

@@

tmp <- melt(d, measure.vars=c('Q_1','Q_2'))
tmp$variable <- gsub("Q_", "Question ", tmp$variable)
p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")

@@

<!-- Field: Q7 -->
3. Do any of your published research papers have publicly archived datasets?

  Response Options:
  1. Yes, datasets from <b>5 or more papers</b> are publicly available on the internet
  2. Yes, datasets from <b>2-4 papers</b> are publicly available on the internet
  3. Yes, a dataset from <b>one paper</b> is publicly available on the internet  
  4. No, none of my paper-related datasets are publicly available on the internet
  5. I've never published a paper based on a dataset collected by me or my co-authors
  6. I'm not sure if any of my papers have publicly available datasets

@@

  Response Options:
  1. Many times
  2. A few times
  3. Once
  4. Never

@@

responses <- c("Requires online public archiving","Recommends online public archiving","Forbids online public archiving")
tmp <- melt(d, measure.vars=paste0('Q_5_', 1:3))
tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("5_", "", .) %>% as.integer]
p <- plot_likert(tmp, response='value', var_x='PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Recommends online public archiving", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
#p <- p + theme(axis.text.x=element_text(angle=-90, size=8))

@@

id_vars <- c('ResponseID','PolicyAdoptedAtPublication','label_PolicyAdoptedAtPublication')
cur_d <- d[,c(id_vars,paste0('Q_6_', 1:6))]
cur_d <- melt(cur_d, id.vars=id_vars) %>% subset(value != "")
cur_d$variable <- NULL

d$Q_6

@@

x <- group_by(cur_d, value, PolicyAdoptedAtPublication, label_PolicyAdoptedAtPublication) %>% dplyr::summarize(N=length(value))
p <- ggplot(x, aes(label_PolicyAdoptedAtPublication, N, group=value, fill=value))+geom_bar(stat="identity", position="dodge")+ylab("Number of Responses")+ylab("JDAP Policy")

p + theme_bw()

@@

levels <- c("Journal supplementary information", "A repository for data or research output", "A personal or lab website",
            "The entire dataset is in the body of the paper", "Not applicable", "Other (please specify)")
cur_d$value <- ordered(cur_d$value, levels=levels)

x <- group_by(cur_d, value, PolicyAdoptedAtPublication, label_PolicyAdoptedAtPublication) %>% dplyr::summarize(N=length(value))
p <- ggplot(x, aes(label_PolicyAdoptedAtPublication, N, group=value, fill=value))+geom_bar(stat="identity", position="dodge")+ylab("Number of Responses")+ylab("JDAP Policy")

p + theme_bw()

@@

@@

Response options:
  i. Strongly Agree
  ii. Agree
  iii. Somewhat Agree
  iv. Neutral
  v. Somewhat Disagree
  vi. Disagree
  vii. Strongly Disagree

@@

```
<!-- Field: Q18 -->
10. Imagine you just found a great journal to target when submitting your next manuscript. You read the Instruction to Authors and discover the journal adheres to the Joint Data Archiving Policy (above). How strongly do you disagree/agree with the following statements? I am worried that ...
	a.  others might do research I am currently working on  <!-- Field: Q18_1 -->
	b.  others might do research I am planning to do  <!-- Field: Q18_2 -->
	c.  others might find errors in my research  <!-- Field: Q18_3  -->
	d.  others might misinterpret my dataset or use it inappropriately  <!-- Field: Q18_4 -->
	e.  I/we might be bothered with a lot of questions by qualified people  <!-- Field: Q18_5 -->
	f.  I/we might be bothered with a lot of questions by unqualified people  <!-- Field: Q18_6 -->
	g.  I/we might not be able to find the data  <!-- Field: Q18_7 -->
	h.  it might take me/us a lot of time to find the data  <!-- Field: Q18_8 -->
	i.  it might take me/us a lot of time to format or document the data  <!-- Field: Q18_9 -->
	j.  it might take me/us a lot of time to submit the data  <!-- Field:  Q18_10-->
	k.  I might lose intellectual property or commercial opportunities  <!-- Field: Q18_11 -->
	l.  Other worries (please specify)  <!-- Field: Q18_12/Q18_12_TEXT -->

@@

<!-- Field: Q21 -->
12. How strongly do you disagree/agree with the following statements? Using datasets collected by investigators outside my research group is important in my research.

@@

@@

## Appendix B: Overview of responses to all questions

## Questions 5
5. To your knowledge, what are the policies of these stakeholders as they apply to online public archiving of the datasets associated with your (month) (year) publication in (journal)? Choose all that apply
        a.  The journal  <!-- Field: Q11_1 -->
        b.  Your funder(s)  <!-- Field: Q11_2 -->
        c.  Your employer or institution  <!-- Field: Q11_3 -->

responses <- c("Requires online public archiving","Recommends online public archiving","Forbids online public archiving")

tmp <- melt(d, measure.vars=paste0('Q_5_',c(1:3) ))
tmp$variable <- gsub("Q_", "Question ", tmp$variable)
p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Recommends online public archiving", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)

@@

## Questions 6
6. Are all datasets associated with your (month) (year) publication in (journal) publicly available online?
a.  ALL datasets are publicly available online   <!-- Field: Q12_1 -->
  b.  SOME but not all of the datasets are publicly available online   <!-- Field: Q12_2 -->
  c.  NONE of the datasets are publicly available online   <!-- Field: Q12_3 -->
  d.  I don't know   <!-- Field: Q12_4 -->
e.  We did not collect any data for that publication   <!-- Field: Q12_5 -->
f. Other (please specify)   <!-- Field: Q12_6/Q12_6_TEXT -->
<!-- TODO: What is d$Q_6_7 ??? -->

```{r, eval=FALSE, fig.width=10, fig.height=5, echo=FALSE}

library(ggplot2)
library(reshape2)
library(plyr)
library(dplyr)
library(vcd)

cnames <- paste0('Q_6_',1:6)
x <- d[,cnames]
new_cnames <- apply(x, 2, function(x) unique(x[x!=""])) 
colnames(x) <- new_cnames
x <- x!=""
x

res <- apply(x, 2, function(c1) apply(x, 2, function(c2) sum(c1&c2) ))
res[lower.tri(res)] <- NA
diag(res) <- NA
res

## Questions 12, 13

```{r, eval=FALSE, fig.width=7, fig.height=5, echo=FALSE}

tmp <- melt(d, measure.vars=c('Q_12','Q_13'))
tmp$variable <- gsub("Q_", "Question ", tmp$variable)
p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")

>>>>

load("./data/JDAP_Survey_Data_Tidy.rda") # loads 'd'
load("./data/Journal_JDAP_Adoption_Dates.rda") # loads 'dates'
load("./data/Invitations_Timing.rda") # loads 'invitation_timing'
interactive_mode <- FALSE
jdap_adoption_dates <- dates

@@

<!--
_(Strongly Agree - Agree - Somewhat Agree - Neutral - Somewhat Disagree - Disagree - Strongly Disagree)_
-->

@@

tmp <- melt(d, measure.vars=c('Q_1'))
tmp$variable <- gsub("Q_", "Question ", tmp$variable)
p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")

@@

<!--
_(Strongly Agree - Agree - Somewhat Agree - Neutral - Somewhat Disagree - Disagree - Strongly Disagree)_
-->

tmp <- melt(d, measure.vars=c('Q_2'))
tmp$variable <- gsub("Q_", "Question ", tmp$variable)
p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")

<!-- Field: Q7 -->
3. Do any of your published research papers have publicly archived datasets?
  a. Yes, datasets from <b>5 or more papers</b> are publicly available on the internet
  b. Yes, datasets from <b>2-4 papers</b> are publicly available on the internet
  c. Yes, a dataset from <b>one paper</b> is publicly available on the internet  
  d. No, none of my paper-related datasets are publicly available on the internet
  e. I've never published a paper based on a dataset collected by me or my co-authors
  f. I'm not sure if any of my papers have publicly available datasets

@@

<!--
  Response Options:
  1. Many times
  2. A few times
  3. Once
  4. Never
-->

@@

facet_labels <- c('Journal', 'Funder(s)', 'Employer or institution')
responses <- c("Requires online public archiving","Recommends online public archiving","Forbids online public archiving")
tmp <- melt(d, measure.vars=paste0('Q_5_', 1:3))
tmp$variable <- facet_labels[gsub("Q_", "", tmp$variable) %>% gsub("5_", "", .) %>% as.integer]
tmp$variable <- factor(tmp$variable, levels=facet_labels)

p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Recommends online public archiving", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
#p <- p + theme(axis.text.x=element_text(angle=-90, size=8))

@@

```{r, fig.width=10, fig.height=5, echo=FALSE, eval=FALSE}
library(dplyr)
library(ggplot2)
library(reshape2)
source("./src/plotLikert.R")

id_vars <- c('ResponseID','PolicyAdoptedAtPublication','label_PolicyAdoptedAtPublication')
cur_d <- d[,c(id_vars,paste0('Q_6_', 1:6))]
cur_d <- melt(cur_d, id.vars=id_vars) %>% %>% subset(value != "")
cur_d$variable <- NULL

@@

tmp <- group_by(cur_d, PolicyAdoptedAtPublication, label_PolicyAdoptedAtPublication, value) %>% dplyr::summarize(N=length(value))  %>% dplyr::mutate(N.total=sum(N), class.Proportion=N/N.total)

p <- ggplot(tmp, aes(label_PolicyAdoptedAtPublication, class.Proportion*100, group=value, fill=value, alpha=value))+geom_bar(stat="identity", position="dodge")+xlab("JDAP Policy")+ylab("Proportion of responses (in %)")
p + theme_bw() + scale_fill_manual(values=c(rep("blue",2), rep("red",2), "grey", "green" )) + scale_alpha_manual(values=c(1,.5, 1,.5, 1,1))

@@

levels <- c("Journal supplementary information", "A repository for data or research output", "A personal or lab website",
            "Not applicable", "The entire dataset is in the body of the paper", "Other (please specify)")
cur_d$value <- ordered(cur_d$value, levels=levels)

tmp <- group_by(cur_d, PolicyAdoptedAtPublication, label_PolicyAdoptedAtPublication, value) %>% dplyr::summarize(N=length(value))  %>% dplyr::mutate(N.total=sum(N), class.Proportion=N/N.total)

p <- ggplot(tmp, aes(label_PolicyAdoptedAtPublication, class.Proportion*100, group=value, fill=value))+geom_bar(stat="identity", position="dodge")+xlab("JDAP Policy")+ylab("Proportion of responses (in %)")
p + theme_bw()

@@

id_vars <- c('ResponseID','PolicyAdoptedAtPublication','label_PolicyAdoptedAtPublication')
cur_d <- d[,c(id_vars,paste0('Q_8_', 1:10))]
cur_d <- melt(cur_d, id.vars=id_vars) %>% subset(value != "")
cur_d$variable <- NULL

levels <- c("The dataset has been submitted to a repository and is currently under embargo",
            "We plan to publicly archive the dataset in the future",
            "We plan to share the dataset upon request",
            "We hadn't considered publicly archiving the dataset",
            "We considered publicly archiving data and decided not to",
            "We wanted to publicly archive the data but were not able to, due to resource limitations",
            "We wanted to publicly archive the data but were not able to, for other reasons",           
            "We wanted to publicly archive the data but were not able to, due to licencing or funder restrictions",
            "Not applicable", "Other (please specify)")
cur_d$value <- ordered(cur_d$value, levels=levels)

tmp <- group_by(cur_d, PolicyAdoptedAtPublication, label_PolicyAdoptedAtPublication, value) %>% dplyr::summarize(N=length(value))  %>% dplyr::mutate(N.total=sum(N), class.Proportion=N/N.total)

p <- ggplot(tmp, aes(label_PolicyAdoptedAtPublication, class.Proportion*100, group=value, fill=value))+geom_bar(stat="identity", position="dodge")+xlab("JDAP Policy")+ylab("Proportion of responses (in %)")
p + theme_bw()

@@

<!--
Response options:
  i. Strongly Agree
  ii. Agree
  iii. Somewhat Agree
  iv. Neutral
  v. Somewhat Disagree
  vi. Disagree
  vii. Strongly Disagree
-->

@@

<!-- Field: Q18 -->
10. Imagine you just found a great journal to target when submitting your next manuscript. You read the Instruction to Authors and discover the journal adheres to the Joint Data Archiving Policy (above). How strongly do you disagree/agree with the following statements? I am worried that ...
	a.  others might do research I am currently working on  <!-- Field: Q18_1 -->
	b.  others might do research I am planning to do  <!-- Field: Q18_2 -->
	c.  others might find errors in my research  <!-- Field: Q18_3  -->
	d.  others might misinterpret my dataset or use it inappropriately  <!-- Field: Q18_4 -->
	e.  I/we might be bothered with a lot of questions by qualified people  <!-- Field: Q18_5 -->
	f.  I/we might be bothered with a lot of questions by unqualified people  <!-- Field: Q18_6 -->
	g.  I/we might not be able to find the data  <!-- Field: Q18_7 -->
	h.  it might take me/us a lot of time to find the data  <!-- Field: Q18_8 -->
	i.  it might take me/us a lot of time to format or document the data  <!-- Field: Q18_9 -->
	j.  it might take me/us a lot of time to submit the data  <!-- Field:  Q18_10-->
	k.  I might lose intellectual property or commercial opportunities  <!-- Field: Q18_11 -->
	l.  Other worries (please specify)  <!-- Field: Q18_12/Q18_12_TEXT -->

responses <- c("Strongly Agree","Strongly Disagree") # response categories from top to bottom
tmp <- melt(d, measure.vars=paste0('Q_10_',1:11 ))
tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("10_", "", .) %>% as.integer]
p <- plot_likert(tmp, response='value', var_x='PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Strongly Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
p <- p + theme(axis.text.x=element_text(angle=-90, size=8))

@@

responses <- c("Strongly Agree","Strongly Disagree") # response categories from top to bottom
tmp <- melt(d, measure.vars=paste0('Q_11_',1:10 ))

tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("11_", "", .) %>% as.integer]
p <- plot_likert(tmp, response='value', var_x='PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Strongly Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
p <- p + theme(axis.text.x=element_text(angle=-90, size=8))

How strongly do you disagree/agree with the following statements?

<!-- Field: Q21 -->
12.  Using datasets collected by investigators outside my research group is important in my research.

tmp <- melt(d, measure.vars=c('Q_12'))
tmp$variable <- gsub("Q_", "Question ", tmp$variable)
p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")

@@

tmp <- melt(d, measure.vars=c('Q_13'))
tmp$variable <- gsub("Q_", "Question ", tmp$variable)
p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")

@@

## Appendix B: JDAP Adoption Dates

```{r, fig.width=7, fig.height=5, echo=FALSE}
library(knitr)

journals_in_dataset <- unique(d$Journal)
relevant_jdap_adoption_dates <- subset(jdap_adoption_dates, Journal %in% journals_in_dataset)

table <- subset(relevant_jdap_adoption_dates, policy == "Required")[,c('JournalName','policy_start_str')]
colnames(table) <- c('Journal', 'Adoption Date of JDAP or Equivalent Policy')
rownames(table) <- NULL
kable(table)

@@
